%
%   ? ћожно ли сделать несколько различных списков литературы или рубрикацию в пределах одного ? 
%

\begin{thebibliography}{10}
\def\selectlanguageifdefined#1{
\expandafter\ifx\csname date#1\endcsname\relax
\else\selectlanguage{#1}\fi}
\providecommand*{\href}[2]{{\small #2}}
\providecommand*{\url}[1]{{\small #1}}
\providecommand*{\BibUrl}[1]{\url{#1}}
\providecommand{\BibAnnote}[1]{}
\providecommand*{\BibEmph}[1]{#1}
\ProvideTextCommandDefault{\cyrdash}{\iflanguage{russian}{\hbox
  to.8em{--\hss--}}{\textemdash}}
\providecommand*{\BibDash}{\ifdim\lastskip>0pt\unskip\nobreak\hskip.2em plus
  0.1em\fi
\cyrdash\hskip.2em plus 0.1em\ignorespaces}
\renewcommand{\newblock}{\ignorespaces}
\makeatletter 
\renewcommand{\@biblabel}[1]{#1.} 
\makeatother

\bibitem{chlipala}
\selectlanguageifdefined{russian}
Chlipala A. Certified programming with dependent types : a pragmatic introduction to the Coq proof assistant / A. Chlipala, 2013. 424 c.

\bibitem{hott}
\selectlanguageifdefined{russian}
\BibEmph{{The Univalent Foundations Program}}. Homotopy Type Theory: Univalent
  Foundations of Mathematics. \BibDash
\newblock Institute for Advanced Study~:
  \url{https://homotopytypetheory.org/book}, 2013.

\bibitem{coq}
\selectlanguageifdefined{russian}
\BibEmph{{Coq Development Team}}. {The Coq Proof Assistant Reference Manual [Ёлектронный ресурс]~: руководство пользовател€}
  \BibDash
\newblock 2012. \BibDash
\newblock –ежим доступа: \BibUrl{https://coq.inria.fr/distrib/current/refman/index.html}.

\bibitem{pierce_coq}
\selectlanguageifdefined{russian}
Pierce B.C. [и др.]. Software Foundations // Version 4.0 (May, 2016) [Ёлектронный ресурс]. URL: http://www.cis.upenn.edu/~bcpierce/sf/current/index.html.

\bibitem{coq_art}
\selectlanguageifdefined{russian}
Bertot Y., Cast?ran P. Interactive Theorem Proving and Program Development / Y. Bertot, P. Cast?ran, Berlin, Heidelberg: Springer Berlin Heidelberg, 2004.
 URL: http://www.cis.upenn.edu/~bcpierce/sf/current/index.html.

%Mercurial  липалы

\bibitem{goldblatt}
\selectlanguageifdefined{russian}
Goldblatt R. Topoi : the categorial analysis of logic / R. Goldblatt, Dover Publications, 2006. 551 c.

\bibitem{ttt}
\selectlanguageifdefined{russian}
Barr M., Wells C. TOPOSES, TRIPLES AND THEORIES 2005. URL: http://www.tac.mta.ca/tac/reprints/articles/12/tr12.pdf

%Mercurial  липалы

\bibitem{tt_geuv}
Geuvers, H. Introduction to Type Theory / Herman Geuvers // Technical
University Eindhoven, The Netherlands \BibDash 2008. \BibDash http://www.cs.ru.nl/
~herman/PUBS/IntroTT.pdf.

\bibitem{harper}
\selectlanguageifdefined{russian}
\BibEmph{Harper,~R.} {Extensionality, intensionality, and BrouwerТs dictum [Ёлектронный ресурс]~: электронна€ стать€} \BibDash
\newblock 2012. \BibDash
\newblock –ежим доступа:
  \BibUrl{http://existentialtype.wordpress.com/2012/08/11/
extensionality-intensionality-and-brouwers-dictum/}.

\end{thebibliography}